### 2013-09-27 evaluation/paper.tex
k-means not capitalizes, minor fixes

\subsection{Superpixel CRFs for Semantic Segmentation}
Our main attention is devoted to the use of conditional random fields for
semantic segmentation.  We use the \textsc{Pascal VOC} and MSRC datasets.
The \textsc{Pascal VOC} has 964 training images, each divided into
around 100 superpixels. There are 20 object categories, and an additional background class. The % TODO check! refer to other part
MSRC-21 dataset has 276 training images, also segmented in around 100 superpixels
each. There are 21 classes in the MSRC-21 dataset.
Each superpixel is represented as an output variable, with the ground truth
obtained by majority vote over the pixels belonging to the superpixel. We
removed all superpixels in which the majority of pixels is labeled ``void'', leading to some samples
having much fewer than 100 variables.
Pairwise potentials are introduced for each pair of neighboring superpixels.
We use the unary and pairwise potentials described in \Secref{semantic_segmentation}:
21 unary features for the \textsc{Pascal VOC} dataset and 63 unary features for the MSRC-21 dataset.
We use the same three pairwise features for both datasets: a constant feature, a color
feature and a feature encoding relative vertical position.
Overall, this results in $21 \cdot  21 + 3 \cdot 21 \cdot 21 = 1764$ parameters
for the potentials on \textsc{Pascal VOC} and $63 \cdot  21 + 3 \cdot 21 \cdot 21 =
2646$ parameters for the potentials on the MSRC-21 dataset.

@@

\begin{table}
    \begin{tabu} to \linewidth{@{}X[1,l]YX[1,c]X[1,c]YY@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset             & {samples} & variables & graph & {dim $\theta$} & {labels}\\
    \cmidrule{1-6}
    MNIST               & 60000   & 1     & none  & 7840  & 10\\
    \textsc{OCR-small}  & 704     & 3--14 & chain & 1444  & 26\\
    \textsc{OCR-large}  & 6173    & 3--14 & chain & 1444  & 26\\
    \textsc{scene-tree} & 1211    & 6     & tree  & 1244  & 2\\
    \textsc{scene-full} & 1211    & 6     & loopy & 1284  & 2\\
    \textsc{yeast-tree} & 1500    & 14    & tree  & 1494  & 2\\
    \textsc{yeast-full} & 1500    & 14    & loopy & 1806  & 2\\
    \textsc{snakes}     & 200     &84--168& loopy & 22275 & 11\\
    MSRC-21             & 276     & 7--113& loopy &  1764 & 21\\
    \textsc{Pascal VOC} & 964     & 8--112& loopy &  2646 & 21\\
    \bottomrule
    \end{tabu}
    \caption{Summary of datasets used in the evaluation. \tablabel{datasets}}
\end{table}

\section{Experiments}
We compare the following algorithms on the above models (see \Secref{learning_algorithms} for details):
\begin{itemize}
    \item Stochastic Subgradient Descent (SSGD) using the Pegasos schedule for step-sizes
    %\item Stochastic Subgradient Descent using the Pegasos schedule: AVERAGING
    \item The $1$-slack cutting plane algorithm without inference caching
    \item The $1$-slack cutting plane algorithm with caching the last 50
        inference results for each sample (see Chapter~\ref{ch:exact_learning}
        for details)
    \item The $n$-slack cutting plane algorithm, where the QP is solved after each sample
    \item The $n$-slack cutting plane algorithm, where the QP is solved every 100 samples
    \item The SZLJSP algorithm with weighted averaging
\end{itemize}

@@

Next, we consider the multi-label task.  The results for the \textsc{yeast} and \textsc{scene}
datasets are shown in \Figref{multi-label-results}. The caching $1$-slack
algorithm is much faster than the non-caching one on both datasets and both
graph structures.
While the two variants of the $n$-slack algorithm are equally fast with respect
to passes over the training data, solving the QP every 100 steps is among the
fastest algorithms, while solving the QP at every step is among the slowest.
We applied this method only to the smaller \textsc{scene} dataset, as applying it on the
\textsc{yeast} dataset was not practical.

@@

The situation is very different when using the linear programming relaxation.
Looking at last two rows of \Figref{snakes_results}, we see that all
algorithms are able to solve the task perfectly. Evaluating on the test-set, all algorithms
achieve an accuracy of around 99.5\%, confirming the models actually learned the task.
Surprisingly, SSGD was very successful on this dataset, even faster then the non-caching $n$-slack
algorithm. Caching provides nearly an order of magnitude speed-up on the dataset.
%
Using branch-and-bound to obtain exact results was not feasible on this dataset.

@@

The last set of experiments is on the segmentation dataset MSRC-21 and \textsc{Pascal
VOC}.  Because of the large number of labels and samples, it is only feasible
to use the fusion move inference algorithm. The results are shown in
\Figref{msrc_pascal_curves}, with the plots in the two upper rows showing results on
MSRC-21, and the tow rows below showing results on \textsc{Pascal VOC}.
First, we notice that all algorithms achieve low (approximate) duality gaps, and none
of the algorithms terminates prematurely. Also, all algorithms achieve a
similar dual objectives and similar training errors after convergence.
In both datasets, the $1$-slack algorithm is somewhat slow in minimizing the
training set error, and the $n$-slack and stochastic algorithms are much
faster. Solving the QP only every 100 steps in the $n$-slack algorithm significantly slows
down learning on both datasets. This is in contrast to the \textsc{yeast} datasets, where the converse was true,
even though \textsc{yeast} has a similar number of training examples to \textsc{Pascal VOC}.

@@

\section{Summary}
From the experiments above, it is clear there is currently \emph{no single best algorithm}.
However, there are some clear trends:
\begin{itemize}
    \item SZLJSP always converges faster than SSGD, with each iteration having
        the same time complexity.  This indicates that SZLJSP should be
        preferred over SSGD, apart from settings with strong memory
        constraints.
    \item In nearly all experiments, caching significantly improved performance
        of the 1-slack cutting plane algorithm.
    \item Initially SZLJSP and even SSGD converge faster than the 1-slack
        cutting plane algorithm, while the 1-slack cutting plane algorithm was
        faster in achieving high precision solutions and guaranteeing low
        duality gap.
    \item The $n$-slack cutting plane algorithm was often fastest to converge in
        terms of passes over the training set, but slow in terms of
        runtime. For problems with very slow inference, the $n$-slack algorithm
        might be a better choice than the others---if the interval between re-solving
        the QP is chosen appropriately.
\end{itemize}
There are however some caveats to our analysis, in particular with respect to
the cutting plane solvers. The performance of the cutting plane algorithms
depends not only on the performance of the QP solver used (in our case
quadratic cone programming), but also on heuristics for pruning variables from
the QP, caching constraints (for the $1$-slack algorithm) and deciding how
often to solve the QP (for the $n$-slack algorithm). Better heuristics could
have a beneficial effect on these algorithms. On the other hand, it is
remarkable how competitive the SZLJSP algorithm is, without the need for any
such implementation tricks. This makes the SZLJSP algorithm very attractive for
the practitioner who does not want to spend much time tuning the
implementation.

>>>>

\subsection{Superpixel CRFs for Semantic Segmentation}
Our main attention is devoted to the use of conditional random fields for
semantic segmentation.  We use the \textsc{Pascal VOC} and MSRC datasets.
The \textsc{Pascal VOC} has $964$ training images, each divided into
around $100$ superpixels. There are $20$ object categories, and an additional background class. The % TODO check! refer to other part
MSRC-21 dataset has $276$ training images, also segmented in around $100$ superpixels
each. There are $21$ semantic classes in the MSRC-21 dataset.
Each superpixel is represented as an output variable, with the ground truth
obtained by majority vote over the pixels belonging to the superpixel. We
removed all superpixels in which the majority of pixels is labeled ``void'', leading to some samples
having much fewer than $100$ variables.
Pairwise potentials are introduced for each pair of neighboring superpixels.
We use the unary and pairwise potentials described in \Secref{semantic_segmentation}:
$21$ unary features for the \textsc{Pascal VOC} dataset and $63$ unary features for the MSRC-21 dataset.
We use the same three pairwise features for both datasets: a constant feature, a color
feature and a feature encoding relative vertical position.
Overall, this results in $21 \cdot  21 + 3 \cdot 21 \cdot 21 = 1764$ parameters
for the potentials on \textsc{Pascal VOC} and $63 \cdot  21 + 3 \cdot 21 \cdot 21 =
2646$ parameters for the potentials on the MSRC-21 dataset.

@@

\begin{table}
    \begin{tabu} to \linewidth{@{}X[1,l]YX[1,c]X[1,c]YY@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset             & {samples} & variables & graph & {dim $\theta$} & {labels}\\
    \cmidrule{1-6}
    MNIST               &$60000$  &$ 1     $ & none  &$7840 $& $10$ \\
    \textsc{OCR-small}  &$704  $  &$ 3--14 $ & chain &$1444 $& $26$ \\
    \textsc{OCR-large}  &$6173 $  &$ 3--14 $ & chain &$1444 $& $26$ \\
    \textsc{scene-tree} &$1211 $  &$ 6     $ & tree  &$1244 $& $ 2$ \\
    \textsc{scene-full} &$1211 $  &$ 6     $ & loopy &$1284 $& $ 2$ \\
    \textsc{yeast-tree} &$1500 $  &$ 14    $ & tree  &$1494 $& $ 2$ \\
    \textsc{yeast-full} &$1500 $  &$ 14    $ & loopy &$1806 $& $ 2$ \\
    \textsc{snakes}     &$200  $  &$84--168$ & loopy &$22275$& $11$ \\
    MSRC-21             &$276  $  &$ 7--113$ & loopy &$ 1764$& $21$ \\
    \textsc{Pascal VOC} &$964  $  &$ 8--112$ & loopy &$ 2646$& $21$ \\
    \bottomrule
    \end{tabu}
    \caption{Summary of datasets used in the evaluation. \tablabel{datasets}}
\end{table}

\section{Experiments}
We compare the following algorithms on the above models (see \Secref{learning_algorithms} for details):
\begin{itemize}
    \item Stochastic Subgradient Descent (SSGD) using the Pegasos schedule for step-sizes
    %\item Stochastic Subgradient Descent using the Pegasos schedule: AVERAGING
    \item The $1$-slack cutting plane algorithm without inference caching
    \item The $1$-slack cutting plane algorithm with caching the last 50
        inference results for each sample (see Chapter~\ref{ch:exact_learning}
        for details)
    \item The $n$-slack cutting plane algorithm, where the QP is solved after each sample
    \item The $n$-slack cutting plane algorithm, where the QP is solved every $100$ samples
    \item The SZLJSP algorithm with weighted averaging
\end{itemize}

@@

Next, we consider the multi-label task.  The results for the \textsc{yeast} and \textsc{scene}
datasets are shown in \Figref{multi-label-results}. The caching $1$-slack
algorithm is much faster than the non-caching one on both datasets and both
graph structures.
While the two variants of the $n$-slack algorithm are equally fast with respect
to passes over the training data, solving the QP every $100$ steps is among the
fastest algorithms, while solving the QP at every step is among the slowest.
We applied this method only to the smaller \textsc{scene} dataset, as applying it on the
\textsc{yeast} dataset was not practical.

@@

The situation is very different when using the linear programming relaxation.
Looking at last two rows of \Figref{snakes_results}, we see that all
algorithms are able to solve the task perfectly. Evaluating on the test-set, all algorithms
achieve an accuracy of around $99.5\%$, confirming the models actually learned the task.
Surprisingly, SSGD was very successful on this dataset, even faster then the non-caching $n$-slack
algorithm. Caching provides nearly an order of magnitude speed-up on the dataset.
%
Using branch-and-bound to obtain exact results was not feasible on this dataset.

@@

The last set of experiments is on the segmentation dataset MSRC-21 and \textsc{Pascal
VOC}.  Because of the large number of labels and samples, it is only feasible
to use the fusion move inference algorithm. The results are shown in
\Figref{msrc_pascal_curves}, with the plots in the two upper rows showing results on
MSRC-21, and the tow rows below showing results on \textsc{Pascal VOC}.
First, we notice that all algorithms achieve low (approximate) duality gaps, and none
of the algorithms terminates prematurely. Also, all algorithms achieve a
similar dual objectives and similar training errors after convergence.
In both datasets, the $1$-slack algorithm is somewhat slow in minimizing the
training set error, and the $n$-slack and stochastic algorithms are much
faster. Solving the QP only every $100$ steps in the $n$-slack algorithm significantly slows
down learning on both datasets. This is in contrast to the \textsc{yeast} datasets, where the converse was true,
even though \textsc{yeast} has a similar number of training examples to \textsc{Pascal VOC}.

@@

\section{Summary}
From the experiments above, it is clear there is currently \emph{no single best algorithm}.
However, there are some clear trends:
\begin{itemize}
    \item SZLJSP always converges faster than SSGD, with each iteration having
        the same time complexity.  This indicates that SZLJSP should be
        preferred over SSGD, apart from settings with strong memory
        constraints.
    \item In nearly all experiments, caching significantly improved performance
        of the $1$-slack cutting plane algorithm.
    \item Initially SZLJSP and even SSGD converge faster than the $1$-slack
        cutting plane algorithm, while the $1$-slack cutting plane algorithm was
        faster in achieving high precision solutions and guaranteeing low
        duality gap.
    \item The $n$-slack cutting plane algorithm was often fastest to converge in
        terms of passes over the training set, but slow in terms of
        runtime. For problems with very slow inference, the $n$-slack algorithm
        might be a better choice than the others---if the interval between re-solving
        the QP is chosen appropriately.
\end{itemize}
There are however some caveats to our analysis, in particular with respect to
the cutting plane solvers. The performance of the cutting plane algorithms
depends not only on the performance of the QP solver used (in our case
quadratic cone programming), but also on heuristics for pruning variables from
the QP, caching constraints (for the $1$-slack algorithm) and deciding how
often to solve the QP (for the $n$-slack algorithm). Better heuristics could
have a beneficial effect on these algorithms. On the other hand, it is
remarkable how competitive the SZLJSP algorithm is, without the need for any
such implementation tricks. This makes the SZLJSP algorithm very attractive for
the practitioner who does not want to spend much time tuning the
implementation.

### 2013-09-27 exact_learning/paper.tex
some moving around of figures and tables
k-means not capitalizes, minor fixes

\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack_again}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$, inference oracle $\hat{I}$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State \label{line_restricted}
            \vspace{-5mm}
            \begin{flalign*}
            \quad\quad    (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi&\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:&\\
            &\theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi&
            \end{flalign*}
            \For {i=1, \dots, k}
                \State
            $\hat{y}\hoch{i} \leftarrow \hat{I}(x\hoch{i}, y\hoch{i}, \theta) \approx \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane_again}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
        \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

\section{Learning SSVMs with Approximate Inference}
In this chapter, we use the $1$-slack cutting plane algorithm, as we found this
algorithm to be most suitable for out approach. Recall the optimization problem
that is solved by the $1$-slack cutting plane algorithm:
\begin{align*}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi \numberthis\label{eq:oneslack_again}\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align*}
For reference, the algorithm described in
\Secref{one_slack}, Algorithm~\ref{alg_one_slack} is reproduced as
Algorithm~\ref{alg_one_slack_again}, with the additional input of an inference algorithm $\hat{I}$, which is called in
line~\ref{get_cutting_plane_again}. We investigate algorithms $\hat{I}$ (often called
separation
oracles in the context) that do not yield the exact maximum here.
There are two groups of inference procedures, as identified by
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $\hat{I}(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane_again}
of Algorithm~\ref{alg_one_slack_again}. An over-generating approach on the other
hand, does solve the loss-augmented prediction in line~\ref{get_cutting_plane_again}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $\hat{I}(x^i, y^i, \theta) \notin \mathcal{Y}$.
%We elaborate on
%the properties of under-generating and over-generating inference procedures in
%Section~\ref{bounds}. %TODO Filler sentence? wat?

@@

It is easy to see that our heuristic runs inference only $O(\log(o^Q -
o_{\W}))$ times more often than the strategy from \citet{joachims2009cutting} in the
worst case.

@@

\subsubsection{Pascal VOC 2010}
For the \textsc{Pascal} VOC 2010 dataset, we follow the procedure from \citet{krahenbuhl2012efficient}
in using the official ``validation'' set as our evaluation set, and splitting the training set again.
We use the unary potentials provided by the same work, and compare only against methods
using the same setup and potentials, \citet{krahenbuhlparameter} and \citet{dann2012pottics}.
Note that state-of-the-art approaches, some not build on the CRF framework, obtain
around a Jaccard Index (also call VOC score) of 40\% , notably \citet{xia2012segmentation}, who 
evaluate on the \textsc{Pascal} VOC 2010 ``test'' set.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figure}
\caption{%
    Visual comparison of the result of exact and approximate learning on
    selected images from the test set.  From left to right: the input image,
    prediction using approximate learning, prediction using exact learning, and
    ground truth.
\figlabel{visual}}
\end{figure*}

>>>>

\section{Learning SSVMs with Approximate Inference}
In this chapter, we use the $1$-slack cutting plane algorithm, as we found this
algorithm to be most suitable for out approach. Recall the optimization problem
that is solved by the $1$-slack cutting plane algorithm:
\begin{align*}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi \numberthis\label{eq:oneslack_again}\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align*}
For reference, the algorithm described in
\Secref{one_slack}, Algorithm~\ref{alg_one_slack} is reproduced as
Algorithm~\ref{alg_one_slack_again}, with the additional input of an inference algorithm $\hat{I}$, which is called in
line~\ref{get_cutting_plane_again}. We investigate algorithms $\hat{I}$ (often called
separation
oracles in the context) that do not yield the exact maximum here.
There are two groups of inference procedures, as identified by
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $\hat{I}(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane_again}
of Algorithm~\ref{alg_one_slack_again}. An over-generating approach on the other
hand, does solve the loss-augmented prediction in line~\ref{get_cutting_plane_again}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $\hat{I}(x^i, y^i, \theta) \notin \mathcal{Y}$.
%We elaborate on
%the properties of under-generating and over-generating inference procedures in
%Section~\ref{bounds}. %TODO Filler sentence? wat?
\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack_again}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$, inference oracle $\hat{I}$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State \label{line_restricted}
            \vspace{-5mm}
            \begin{flalign*}
            \quad\quad    (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi&\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:&\\
            &\theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi&
            \end{flalign*}
            \For {i=1, \dots, k}
                \State
            $\hat{y}\hoch{i} \leftarrow \hat{I}(x\hoch{i}, y\hoch{i}, \theta) \approx \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane_again}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
        \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

@@

It is easy to see that our heuristic runs inference only $O(\log(o^Q -
o_{\W}))$ times more often than the strategy of \citet{joachims2009cutting} in the
worst case.

@@

\subsubsection{Pascal VOC 2010}
For the \textsc{Pascal} VOC 2010 dataset, we follow the procedure of \citet{krahenbuhl2012efficient}
in using the official ``validation'' set as our evaluation set, and splitting the training set again.
We use the unary potentials provided by the same work, and compare only against methods
using the same setup and potentials, \citet{krahenbuhlparameter} and \citet{dann2012pottics}.
Note that state-of-the-art approaches, some not build on the CRF framework, obtain
around a Jaccard Index (also call VOC score) of 40\% , notably \citet{xia2012segmentation}, who 
evaluate on the \textsc{Pascal} VOC 2010 ``test'' set.

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=\linewidth]{figure}
\caption{%
    Visual comparison of the result of exact and approximate learning on
    selected images from the test set.  From left to right: the input image,
    prediction using approximate learning, prediction using exact learning, and
    ground truth.
\figlabel{visual}}
\end{figure*}

### 2013-09-27 intro.tex
k-means not capitalizes, minor fixes

\section{List of Contributions}
This thesis contains the following contributions:
\begin{itemize}
\item Introducing a clustering algorithm that improves upon widely used
    approaches from the literature. Our algorithm yields better clusterings in
    terms of known classes on a wide range of standard datasets.
\item Demonstrating a scalable algorithm for weakly supervised object class
    segmentation.  The proposed method is able to learn to segment complex object
    classes using image annotation alone.
\item Providing a general and efficient open source software framework for
    structured prediction. 
\item Analysing max-margin learning algorithms with exact or approximate
    inference in different applications. We give a thorough evaluation of
    all major SSVM learning algorithms, using a wide array of application.
\item Showing that exact learning for semantic segmentation and object class
    segmentation is possible in practice, even in loopy graphs. We combine
    fast inference, caching and inference algorithms which certify optimality
    to learn a $1$-slack SSVM.
\item Learning 3D relations of semantic structure categories for indoor scenes.
    We extend the CRF approach to learning spacial relations from RGB-D data and
    improve upon the state-of-the-art in semantic annotation on the NYU V2 dataset
    of indoor scenes.
\end{itemize}

>>>>

\section{List of Contributions}
This thesis contains the following contributions:
\begin{itemize}
\item Introducing a clustering algorithm that improves upon widely used
    approaches from the literature. Our algorithm yields better clusterings in
    terms of known classes on a wide range of standard datasets.
\item Demonstrating a scalable algorithm for weakly supervised object class
    segmentation.  The proposed method is able to learn to segment complex object
    classes using image annotation alone.
\item Providing a general and efficient open source software framework for
    structured prediction. 
\item Analysing max-margin learning algorithms with exact and approximate
    inference in different applications. We give a thorough evaluation of
    all major SSVM learning algorithms in a wide array of application.
\item Showing that exact learning for semantic segmentation and object class
    segmentation is possible in practice, even in loopy graphs. We combine
    fast inference, caching and inference algorithms which certify optimality
    to learn a $1$-slack SSVM.
\item Learning 3D relations of semantic structure categories for indoor scenes.
    We extend the CRF approach to learning spacial relations from RGB-D data and
    improve upon the state-of-the-art in semantic annotation on the NYU V2 dataset
    of indoor scenes.
\end{itemize}
